Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-05 manuscript-chicago.Rmd
Redacting

author:
  - name          : "Megan Chiovaro"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
    email         : "megan.chiovaro@uconn.edu"
  - name          : "Alexandra Paxton"
    affiliation   : "1,2,*"
  - name          : "Leah C. Windsor"
    affiliation   : "3,*"

affiliation:
  - id            : "1"
    institution   : "Center for the Ecological Study of Perception and Action, University of Connecticut"
  - id            : "2"
    institution   : "Department of Psychological Sciences, University of Connecticut"
  - id            : "3"
    institution   : "University of Memphis"
  - id            : "*"
    institution   : "Equal author contributions"

@@

keywords          : "social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring"
wordcount         : "X"

@@

@@

This work was completed in part as coursework done by lead author M. Chiovaro in
the “Applications of Nonlinear Time Series Analysis” graduate course at the
University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
Harrison).

>>>>

author:
    - name          : "[author names redacted for blind review]"
#   - name          : "Megan Chiovaro"
#     affiliation   : "1, 2"
#     corresponding : yes    # Define only one corresponding author
#     address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
#     email         : "megan.chiovaro@uconn.edu"
#   - name          : "Alexandra Paxton"
#     affiliation   : "1,2,*"
#   - name          : "Leah C. Windsor"
#     affiliation   : "3,*"
# 
# affiliation:
#   - id            : "1"
#     institution   : "Center for the Ecological Study of Perception and Action, University of Connecticut"
#   - id            : "2"
#     institution   : "Department of Psychological Sciences, University of Connecticut"
#   - id            : "3"
#     institution   : "University of Memphis"
#   - id            : "*"
#     institution   : "Equal author contributions"

@@

keywords          : "social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring"
wordcount         : "10981"

@@

This work is a reproducible manuscript. All code and analyses can be found at:
[redacted for blind review].

@@

[redacted for blind review]

<!-- This work was completed in part as coursework done by lead author M. Chiovaro in -->
<!-- the “Applications of Nonlinear Time Series Analysis” graduate course at the -->
<!-- University of Connecticut (co-taught by coauthor A. Paxton and Steven J. -->
<!-- Harrison). -->
